---
output:
  html_document: default
  word_document: default
---
# Predicting and Visualizing Thermal Habitat: `thermopic`

The `thermopic` R package provides functionality for predicting and visualizing the seasonal availability of thermal habitat in lakes.

## Installation

Installation is easiest from an `R` commandline using the `devtools` package.
```{r, eval=FALSE}
devtools::install_github('stevencarlislewalker/thermopic')
```

It might be necessary to preceed this first step by installing `devtools`.
```{r, eval=FALSE}
install.packages('devtools')
```

Once the package is installed, it may be loaded using the `library` function.
```{r}
library(thermopic)
```

## Setting up the directory structure

The `thermopic` package runs within a project directory. Here we create a temporary directory for this tutorial using the `temporary_thermopic_directory` function.
```{r}
root = temporary_thermopic_directory()
```

In this case the temporary directory is located here.
```{r, echo=FALSE}
root
```

We now use `thermopic`'s `setup_directory` function to create the required directory structure for our project.  This function allows some flexibility in how input data are specified.  Here we use the defaults, which extract sample data contained within the package.
```{r}
setup_directory(root, overwrite = TRUE)
```

We may inspect this structure using `thermopic`s `print_directory_tree` utility function.
```{r}
print_directory_tree(root)
```

## Running the model and report functions

Now that the structure is in place, one may fit the thermopic model.
```{r}
fitted_thermopic_model = thermopic_model(
  path = root,
  laked = '1_lake.csv',
  sited = '2_Climate.csv'
)
```

And create the report as well as the thermopic images themselves.  For speed we restrict the number of lakes to process to `5`.
```{r}
thermopic_report_data = thermopic_report(
  path = root,
  spaced = fitted_thermopic_model$STM,
  Options = '0_User_Options.csv',
  Nlakes_test = 5,
  show_progress_bar = FALSE
)
```

## Inspecting the updated directory structure

Here we see the resulting outputs including the images in `jpeg` format files.
```{r, echo=FALSE}
print_directory_tree(root)
```

```{r, echo=FALSE}
unlink(root)
```

For a more detailed introduction see this tutorial.
