# Tutorial for using the `thermopic` package

```{r}
library(thermopic)
```

## Setting up the project directory structure -- `setup_directory`

The `setup_directory` function takes two specially-formatted data frames as arguments.  The first describes the geography, morphometry, and water quality of lakes.  The second describes the climate of each lake over a particular time period.  There are examples of these files included in the `thermopic` package.  To obtain the location of these files within your installation of `thermopic`, one may use the `system.file` function.
```{r}
lake_csv = system.file('extdata/1_Lake.csv', package = 'thermopic')
climate_csv = system.file('extdata/2_Climate.csv', package = 'thermopic')
print(lake_csv)
print(climate_csv)
```


Here we read these example data frames and print out the first six records of each.
```{r}
lake_example = read.csv(lake_csv)
climate_example = read.csv(climate_csv)
head(lake_example)
head(climate_example)
```

The `setup_directory` function is used to produce the required directory structure for a thermopic project, and inject the lake and climate data into the appropriate place within this structure.
```{r}
setup_directory(path = '../misc/tutorial_project', 
                Lake = lake_csv,
                Climate = climate_csv,
                overwrite = TRUE)
print_directory_tree('../misc/tutorial_project')
```

## Fitting the seasonal temperature model -- `thermopic_model`

```{r}
thermopic_model(path = '../misc/tutorial_project')
```

## Visualizing thermal habitat in lakes -- `thermopic_report`
